---
title: "Untitled"
author: "Chen Zihao 915490404"
date: "2017年12月9日"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE#fig.width=5,fig.height=3.5,fig.align='center'
                      ,fig.path='Figs/'
                      )
```

1.	Introduction

2.	A description of
(i)	the relevant background of the topic;  
(ii)	questions of interest
(iii)	the motivation of the project i.e., why other people should be interested.
You should also briefly describe the data.

3.	Methods and Results:
4.	Conclusions and Discussion
5.	Appendices
6.	References

```{r}
Data=read.csv('G:/movie_metadata.csv',header=TRUE)
```

Replace the missing values in the variable frame by ’NA’ and drop the old class ‘’.
```{r}
Data=Data[,-c(2,7,11,12,15,17,18)]#delete all the names
summary(Data)
```


```{r}

sapply(Data,class)#to check which variable is a factor

#repalce ’’ with NA for all the factor variable
is.na(Data$color)=which(Data$color=='') 
is.na(Data$language)=which(Data$language=='')
is.na(Data$genres)=which(Data$genres=='')
is.na(Data$country)=which(Data$country=='')
is.na(Data$content_rating)=which(Data$content_rating=='')

Data$color=droplevels(Data$color)
Data$language=droplevels(Data$language)
Data$genres=droplevels(Data$genres)
Data$country=droplevels(Data$country)
Data$content_rating=droplevels(Data$content_rating)
```


```{r}
#Action	Adventure	Fantasy	Sci-Fi Thriller Documentary	Romance	Animation	Comedy Family	Musical	Mystery	Western	Drama	History Sport	Crime	Horror War Biography Music....but
#ignore the genres with small number. there are 1 Game-Show 2 Reality-TV 3 News 5 Short 6 Film-Noir 		
Data$Action=sapply(Data$genres,function(x){grepl(x,'Action')})
Data$Adventure=sapply(Data$genres,function(x){grepl(x,'Adventure')})
Data$Fantasy=sapply(Data$genres,function(x){grepl(x,'Fantasy')})
Data$Sci.Fi=sapply(Data$genres,function(x){grepl(x,'Sci-Fi')})
Data$Thriller=sapply(Data$genres,function(x){grepl(x,'Thriller')})
Data$Documentary=sapply(Data$genres,function(x){grepl(x,'Documentary')})
Data$Romance=sapply(Data$genres,function(x){grepl(x,'Romance')})
Data$Animation=sapply(Data$genres,function(x){grepl(x,'Animation')})
Data$Comedy=sapply(Data$genres,function(x){grepl(x,'Comedy')})
Data$Family=sapply(Data$genres,function(x){grepl(x,'Family')})
Data$Musical=sapply(Data$genres,function(x){grepl(x,'Musical')})
Data$Mystery=sapply(Data$genres,function(x){grepl(x,'Mystery')})
Data$Western=sapply(Data$genres,function(x){grepl(x,'Western')})
Data$Drama=sapply(Data$genres,function(x){grepl(x,'Drama')})
Data$History=sapply(Data$genres,function(x){grepl(x,'History')})
Data$Sport=sapply(Data$genres,function(x){grepl(x,'Sport')})
Data$Crime=sapply(Data$genres,function(x){grepl(x,'Crime')})
Data$Horror=sapply(Data$genres,function(x){grepl(x,'Horror')})
Data$War=sapply(Data$genres,function(x){grepl(x,'War')})
Data$Biography=sapply(Data$genres,function(x){grepl(x,'Biography')})
Data$Music=sapply(Data$genres,function(x){grepl(x,'Music')})
```

```{r}
Data=Data[,-8]
a=lm(gross~.,data=Data)
summary(a)
```
